[dcpo_demsupport]

### 2020-08-02 paper/dcpo_demsupport.Rmd
adding dotwhisker preload

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  plm, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse # data wrangling
)

@@

(dwplot(df_result_dcpo, by_2sd = FALSE)) %>% 
  relabel_predictors(c(`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)")) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") + 
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  plm, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, # data wrangling
  dotwhisker # visualization
)

@@

dwplot(df_result_dcpo, by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
      `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
      `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
      `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
      `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
      `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
      `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
      `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
      #there's a lag in the replication file
      `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")
